High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-05 notebooks/poc.qmd
some intial work on illustration

ces = Dict{Any,Any}()
plts = []
for (name, generator) in generator_dict
    ce = generate_counterfactual(
        x_factual, target, counterfactual_data, M, generator;
        initialization=:identity, 
        converge_when=:generator_conditions,
        decision_threshold=γ,
    )
    plt = Plots.plot(ce, title=name, alpha=0.2, cbar=false, axis=nothing, length_out=10)
    if name == "ECCCo"
        _X = distance_from_energy(ce, return_conditionals=true)
        Plots.scatter!(
            _X[1,:],_X[2,:], color=:purple, shape=:star5, 
            ms=10, label="x̂|$target", alpha=0.5
        )
    end
    push!(plts, plt)
    ces[name] = ce
end
plt = Plots.plot(plts..., size=(500,520))
display(plt)
savefig(plt, joinpath(output_images_path, "poc.png"))
```

```{julia}
ce = ces["ECCCo"]
```

>>>>

ces = Dict{Any,Any}()
plts = []
for (name, generator) in generator_dict
    ce = generate_counterfactual(
        x_factual, target, counterfactual_data, M, generator;
        initialization=:identity, 
        converge_when=:generator_conditions,
        decision_threshold=γ,
    )
    plt = Plots.plot(ce, title=name, alpha=0.2, cbar=false, axis=nothing, length_out=10)
    if name == "ECCCo"
        _X = distance_from_energy(ce, return_conditionals=true)
        Plots.scatter!(
            _X[1,:],_X[2,:], color=:purple, shape=:star5, 
            ms=10, label="x̂|$target", alpha=0.1
        )
    end
    push!(plts, plt)
    ces[name] = ce
end
plt = Plots.plot(plts..., size=(500,520))
display(plt)
savefig(plt, joinpath(output_images_path, "poc.png"))
```

```{julia}
ce = ces["ECCCo"]
using CounterfactualExplanations.Generators: ℓ

# loss
function f1(x)
    _ce = deepcopy(ce)
    _ce.s′ = x
    return - ℓ(_ce.generator, _ce)
end

# cost
function f2(x)
    _ce = deepcopy(ce)
    _ce.s′ = x
    λ = _ce.generator.λ[1]
    _loss = _ce.generator.penalty[1]
    return - λ * _loss(_ce)
end

# set size
function f3(x)
    _ce = deepcopy(ce)
    _ce.s′ = x
    λ = _ce.generator.λ[2]
    _loss = _ce.generator.penalty[2]
    return - λ * _loss(_ce)
end

# distance from energy
function f4(x)
    _ce = deepcopy(ce)
    _ce.s′ = x
    λ = _ce.generator.λ[3]
    _loss = _ce.generator.penalty[3]
    return - λ * _loss(_ce)
end

# Helper function:
meshgrid(x, y) = (repeat(x, outer=length(y)), repeat(y, inner=length(x)))

xlims, ylims = extrema(X, dims=2)
xrange = range(xlims..., length=10)
yrange = range(ylims..., length=10)

x1, x2 = meshgrid(xrange, yrange)
inputs = zip(x, y)

u = []
v = []

scale = 0.1
for (x, y) in inputs
    push!(u, scale * gradient(f2, [x, y][:,:])[1][1])
    push!(v, scale * gradient(f2, [x, y][:,:])[1][2])
end

Plots.plot(xlims=xlims, ylims=ylims)
Plots.scatter!(counterfactual_data)
Plots.quiver!(x1, x2, quiver=(u, v))
```
